Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
Extend case study 2

\begin{minted}[breakindent=0em,linenos=false,xleftmargin=0em,breakafter=)]{fortran}
!=stencil readOnce,(forward(depth=1,dim=3,irreflexive))*(backward(depth=1,dim=1))*(backward(depth=1,dim=2))+(forward(depth=1,dim=3))*(backward(depth=1,dim=1))*(reflexive(dim=2))+(forward(depth=1,dim=3))*(backward(depth=1,dim=1,irreflexive))*(backward(depth=1,dim=2,irreflexive))+(forward(depth=1,dim=3))*(backward(depth=1,dim=2))*(reflexive(dim=1))+(backward(depth=1,dim=1))*(backward(depth=1,dim=2,irreflexive))*(reflexive(dim=3))+(backward(depth=1,dim=1,irreflexive))*(backward(depth=1,dim=2))*(reflexive(dim=3))::x
\end{minted}
%
This specifies the access pattern to a 3-dimensional array (which we have renamed to be called \texttt{x}). The array is accessed 8 times in the computation. We tried introducing indexing errors by changing the offset in one dimension of one of the references to \texttt{x}. For example changing \mintinline{fortran}{x(i+1,j,k)} to \mintinline{fortran}{x(i,j,k)} or \mintinline{fortran}{x(i-1,j,k)}. There are 48 possible errors of this type of which we found only 6 were not detected by the specification checking.
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught

\section{Discussion}
\label{sec:discussion}

>>>>

\begin{minted}[breakindent=0em,linenos=false,xleftmargin=0em,breakafter=)]{fortran}
!=stencil readOnce,(forward(depth=1,dim=3,irreflexive))*(backward(depth=1,dim=1))*(backward(depth=1,dim=2))+(forward(depth=1,dim=3))*(backward(depth=1,dim=1))*(reflexive(dim=2))+(forward(depth=1,dim=3))*(backward(depth=1,dim=1,irreflexive))*(backward(depth=1,dim=2,irreflexive))+(forward(depth=1,dim=3))*(backward(depth=1,dim=2))*(reflexive(dim=1))+(backward(depth=1,dim=1))*(backward(depth=1,dim=2,irreflexive))*(reflexive(dim=3))+(backward(depth=1,dim=1,irreflexive))*(backward(depth=1,dim=2))*(reflexive(dim=3))::x
\end{minted}
%
This specifies the access pattern to a 3-dimensional array (which we have renamed to be called \texttt{x}). The array is accessed 8 times in the computation. We tried introducing indexing errors by changing the offset in one dimension of one of the references to \texttt{x}. For example changing \mintinline{fortran}{x(i+1,j,k)} to \mintinline{fortran}{x(i,j,k)} or \mintinline{fortran}{x(i-1,j,k)}.

There are 48 possible errors of this type of which we found only 6 were not 
detected by the specification checking. The reason is that the inferred
specification describes a family of access patterns. Some offset errors
produce a stencil computation that belongs to the same family and goes
undetected.

One of the reasons this specification can catch many offset errors is that it is
a \texttt{readOnce} specification. This prevents offset errors leading to
duplicate access patterns be caught even if the resulting set of accesses are
part of the same family.
% /um/trunk/src/atmosphere/diffusion_and_filtering/turb_smagorinsky.F90
% Tried introducing indexing errors replacing one of the indices of cx_rho_instance with -1,0,+1
% 42 cases were caught
% 6 cases were not caught
\section{Discussion}
\label{sec:discussion}
